CdGF_aucrf

### 2016-09-23 code/CdGF_AUCRF.Rmd
refine line plots for aucrf

#random forest regression model to determine Day 0 OTU correlated with increased CFU
seed <- 18
n_trees <- 2001
set.seed(seed)

@@

# create RF model
rf_early_aucrf <- AUCRF(Euth_Early ~ ., data = Predict_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
random_roc <- roc(sample(c(1,0), length(otu_euth_probs[ , 2]), replace = T) ~ otu_euth_probs[ , 2])

@@

#### 10-fold Cross validated - 10 repetitions
iters <- 100
cv10f_aucs <- c()
cv10f_all_resp <- c()
cv10f_all_pred <- c()
for(j in 1:iters){
  sampling <- sample(1:nrow(aucrf_data),nrow(aucrf_data),replace=F)
  cv10f_probs <- rep(NA,nrow(aucrf_data))
  for(i in seq(1,nrow(aucrf_data),5)){
    train <- aucrf_data[sampling[-(i:(i+4))],]
    test <- aucrf_data[sampling[i:(i+4)],]
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  cv10f_roc <- roc(aucrf_data$Euth_Early~cv10f_probs)
  cv10f_all_pred <- c(cv10f_all_pred, cv10f_probs)
  cv10f_all_resp <- c(cv10f_all_resp, aucrf_data$Euth_Early)
  cv10f_aucs[j] <- cv10f_roc$auc
}
cv10f_roc <- roc(cv10f_all_resp~cv10f_all_pred)

#### leave-one-out
LOO_probs <- NULL
LOO_probs <- sapply(1:nrow(aucrf_data), function(i){
 train <- aucrf_data[-i,]
  test <- aucrf_data[i,]
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOO_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOO_roc <- roc(aucrf_data$Euth_Early~LOO_probs)

@@

LOcO_probs <- NULL
LOcO_probs <- sapply(1:length(cage_list), function(i){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[-by_cage,]
  test <- LOcO_predict[by_cage,]
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOcO_probs <- unlist(LOcO_probs)
LOcO_roc <- roc(aucrf_data$Euth_Early~LOcO_probs)

#### Random - 10-fold Cross validated - 10 repetitions
ran_aucrf_data <- cbind(Euth_Early = factor(sample(Predict_early_euth_df$Euth_Early, 
                                                     nrow(Predict_early_euth_df))),
                             Predict_early_euth_df[,rf_early_aucrf$Xopt])
ran_cv10f_aucs <- c()
ran_cv10f_all_resp <- c()
ran_cv10f_all_pred <- c()
for(j in 1:iters){
  sampling <- sample(1:nrow(ran_aucrf_data),nrow(ran_aucrf_data),replace=F)
  ran_cv10f_probs <- rep(NA,nrow(ran_aucrf_data))
  for(i in seq(1,nrow(ran_aucrf_data),5)){
    train <- ran_aucrf_data[sampling[-(i:(i+4))],]
    test <- ran_aucrf_data[sampling[i:(i+4)],]
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    ran_cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  ran_cv10f_roc <- roc(ran_aucrf_data$Euth_Early~ran_cv10f_probs)
  ran_cv10f_all_pred <- c(ran_cv10f_all_pred, ran_cv10f_probs)
  ran_cv10f_all_resp <- c(ran_cv10f_all_resp, ran_aucrf_data$Euth_Early)
  ran_cv10f_aucs[j] <- ran_cv10f_roc$auc
}
ran_cv10f_roc <- roc(ran_cv10f_all_resp~ran_cv10f_all_pred)

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='red', lwd=2, add=T, lty=2)
plot(ran_cv10f_roc, col='orange', lwd=3, add=T, lty=2)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('Random (AUC: %.3g)',ran_cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,3,0,0), lwd=2, col=c('black','blue','red','gray','orange'), bty='n')
```

@@

* When adding diversity and CFU, invsimpson and cfu appear as features, but when cfu is removed, invsimpson is no longer a predictor

@@

```{r Random_validation, fig.width=6, fig.height=5, results= 'hide'}
#create dataframe for RF-classification
Validate_early_euth_df <- Predict_early_euth_df
Validate_early_euth_df$Euth_Early <- sample(Validate_early_euth_df$Euth_Early)

# create RF model
rf_early_aucrf <- AUCRF(Euth_Early ~ ., data = Validate_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')

otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Validate_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])

aucrf_data <- Validate_early_euth_df[,c('Euth_Early',rf_early_aucrf$Xopt)]

#### 10-fold Cross validated - 10 repetitions
iters <- 100
cv10f_aucs <- c()
cv10f_all_resp <- c()
cv10f_all_pred <- c()
for(j in 1:iters){
  sampling <- sample(1:nrow(aucrf_data),nrow(aucrf_data),replace=F)
  cv10f_probs <- rep(NA,nrow(aucrf_data))
  for(i in seq(1,nrow(aucrf_data),5)){
    train <- aucrf_data[sampling[-(i:(i+4))],]
    test <- aucrf_data[sampling[i:(i+4)],]
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  cv10f_roc <- roc(aucrf_data$Euth_Early~cv10f_probs)
  cv10f_all_pred <- c(cv10f_all_pred, cv10f_probs)
  cv10f_all_resp <- c(cv10f_all_resp, aucrf_data$Euth_Early)
  cv10f_aucs[j] <- cv10f_roc$auc
}
cv10f_roc <- roc(cv10f_all_resp~cv10f_all_pred)

#### leave-one-out
LOO_probs <- NULL
LOO_probs <- sapply(1:nrow(aucrf_data), function(i){
 train <- aucrf_data[-i,]
  test <- aucrf_data[i,]
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOO_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOO_roc <- roc(aucrf_data$Euth_Early~LOO_probs)

#### leave-one-cage-out
LOcO_df <- cbind(cage_id = sample(meta_file[meta_file$day %in% 0, 'cage_id'],
                                  nrow(Validate_early_euth_df)),
                 Validate_early_euth_df[ , c('Euth_Early', rf_early_aucrf$Xopt)])
cage_list <- as.character(unique(LOcO_df$cage_id))

LOcO_probs <- NULL
LOcO_probs <- sapply(1:length(cage_list), function(i){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[-by_cage,]
  test <- LOcO_predict[by_cage,]
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_probs[[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOcO_probs <- unlist(LOcO_probs)
LOcO_roc <- roc(aucrf_data$Euth_Early~LOcO_probs)

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='red', lwd=2, add=T, lty=2)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,0,0), lwd=2, col=c('black','blue','red','gray'), bty='n')
```

```{r Random_valid OTUs, fig.width=10, fig.height=8}
layout(matrix(c(1,1,1,1,4,4,4,
                2,2,2,5,3,3,3,
                2,2,2,5,3,3,3), nrow=3, byrow = TRUE))

#AUCRF curve
par(mar=c(5,5,1.5,1))
plot(rf_early_aucrf)
#mtext('A', at=-90, font=2, side=3)

#Abundance stripchart or most predictive otus
euth_otus <- rev(rf_early_aucrf$Xopt)
early_abunds <- Validate_early_euth_df[Validate_early_euth_df$Euth_Early==0, euth_otus]/10000 + 1e-4
late_abunds <- Validate_early_euth_df[Validate_early_euth_df$Euth_Early==1, euth_otus]/10000 + 1e-4

par(mar=c(4, 9, 1, 1))
plot(1, type="n", ylim=c(0,length(euth_otus)*2), xlim=c(1e-4,1e-2), log="x", ylab="", xlab="Relative Abundance (%)", xaxt="n", yaxt="n")
index <- 1
for(i in euth_otus){
  stripchart(at=index-0.35, jitter(early_abunds[,i], amount=1e-5), pch=21, bg="royalblue1", method="jitter", jitter=0.2, add=T, cex=1, lwd=0.5)
  stripchart(at=index+0.35, jitter(late_abunds[,i], amount=1e-5), pch=21, bg="orange", method="jitter", jitter=0.2, add=T, cex=1, lwd=0.5)
  segments(mean(early_abunds[,i]),index-0.7,mean(early_abunds[,i]),index, lwd=3)
  segments(mean(late_abunds[,i]),index+0.7,mean(late_abunds[,i]),index, lwd=3)
  index <- index + 2
}
axis(2, at=seq(1,index-2,2), labels=euth_tax[euth_otus, 'tax_label'], las=1, line=-0.5, tick=F, cex.axis=0.8)
axis(1, at=c(1e-4, 1e-3, 1e-2), label=c("0", "0.1", "1"))
legend('topright', legend=c("Mild", "Severe"), pch=c(21, 21), pt.bg=c("orange","royalblue1"), cex=0.7)
#mtext('C', at=1e-7, font=2, side=3)

>>>>

#random forest regression model to determine Day 0 OTU correlated with increased CFU
seed <- 1
n_trees <- 2001
iters <- 100

@@

# create RF model
set.seed(seed)
rf_early_aucrf <- AUCRF(Euth_Early ~ ., data = Predict_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
otu_euth_probs <- predict(rf_early_aucrf$RFopt, type = 'prob')
otu_euth_roc <- roc(Predict_early_euth_df$Euth_Early ~ otu_euth_probs[ , 2])
set.seed(seed)
random_roc <- roc(sample(c(1,0), length(otu_euth_probs[ , 2]), replace = T) ~ otu_euth_probs[ , 2])

@@

#### 10-fold Cross validated - 10 repetitions
cv10f_aucs <- c()
cv10f_all_resp <- c()
cv10f_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  sampling <- sample(1:nrow(aucrf_data),nrow(aucrf_data),replace=F)
  cv10f_probs <- rep(NA,nrow(aucrf_data))
  for(i in seq(1,nrow(aucrf_data),5)){
    train <- aucrf_data[sampling[-(i:(i+4))],]
    test <- aucrf_data[sampling[i:(i+4)],]
    set.seed(seed)
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  cv10f_roc <- roc(aucrf_data$Euth_Early~cv10f_probs)
  cv10f_all_pred <- c(cv10f_all_pred, cv10f_probs)
  cv10f_all_resp <- c(cv10f_all_resp, aucrf_data$Euth_Early)
  cv10f_aucs[j] <- cv10f_roc$auc
}
cv10f_roc <- roc(cv10f_all_resp~cv10f_all_pred)

#### leave-one-out
LOO_probs <- NULL
LOO_probs <- sapply(1:nrow(aucrf_data), function(i){
 train <- aucrf_data[-i,]
  test <- aucrf_data[i,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOO_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOO_roc <- roc(aucrf_data$Euth_Early~LOO_probs)

@@

LOcO_probs <- NULL
LOcO_probs <- sapply(1:length(cage_list), function(i){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[-by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcO_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOcO_probs <- unlist(LOcO_probs)
LOcO_roc <- roc(aucrf_data$Euth_Early~LOcO_probs)

#### Random - 10-fold Cross validated - 10 repetitions

set.seed(seed)
ran_outcome_data <- cbind(Euth_Early = factor(sample(Predict_early_euth_df$Euth_Early,  
                                                     nrow(Predict_early_euth_df))), 
                             Predict_early_euth_df[,rf_early_aucrf$Xopt]) 
predict_random <-  predict(rf_early_aucrf$RFopt, ran_outcome_data, type = 'prob')[,2]
predict_random_roc <- roc(ran_outcome_data$Euth_Early ~ predict_random)

ran_cv10f_aucs <- c()
ran_cv10f_all_resp <- c()
ran_cv10f_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  sampling <- sample(1:nrow(aucrf_data),nrow(aucrf_data),replace=F)
  ran_cv10f_probs <- rep(NA,nrow(aucrf_data))
  for(i in seq(1,nrow(aucrf_data),5)){
    train <- aucrf_data[sampling[-(i:(i+4))],]
    test <- ran_outcome_data[sampling[i:(i+4)],]
    set.seed(seed)
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    ran_cv10f_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  ran_cv10f_roc <- roc(ran_outcome_data$Euth_Early~ran_cv10f_probs)
  ran_cv10f_all_pred <- c(ran_cv10f_all_pred, ran_cv10f_probs)
  ran_cv10f_all_resp <- c(ran_cv10f_all_resp, ran_outcome_data$Euth_Early)
  ran_cv10f_aucs[j] <- ran_cv10f_roc$auc
}
ran_cv10f_roc <- roc(ran_cv10f_all_resp~ran_cv10f_all_pred)

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_euth_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10f_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOO_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcO_roc, col='purple', lwd=2, add=T, lty=3)
plot(ran_cv10f_roc, col='orange', lwd=2, add=T, lty=1)
plot(predict_random_roc, col='red', lwd=2, add=T, lty=3)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_euth_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOO_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcO_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10f_roc$auc),
                               sprintf('Random (AUC: %.3g)',ran_cv10f_roc$auc),
                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_euth_roc,LOO_roc)$p.value),
                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_euth_roc,cv10f_roc)$p.value)
),lty=c(1,2,2,1,3,0,0), lwd=2, col=c('black','blue','red','gray','orange'), bty='n')
```

@@

* When adding enterotype, diversity, and CFU, invsimpson and cfu appear as features, but when cfu is removed, invsimpson is no longer a predictor

@@

```{r Random_validation, fig.width=6, fig.height=5, results= 'hide'}

# boruta feature selection
#set.seed(seed)
#Boruta(Euth_Early ~ ., data = Validate_early_euth_df, maxRuns = 200)

#create dataframe for random RF-classification
Validate_early_euth_df <- Predict_early_euth_df
set.seed(seed)
Validate_early_euth_df$Euth_Early <- sample(Predict_early_euth_df$Euth_Early)

# create RF model
set.seed(seed)
rf_random_aucrf <- AUCRF(Euth_Early ~ ., data = Validate_early_euth_df,
                              ntree = n_trees, pdel = 0.05, ranking = 'MDA')
otu_random_probs <- predict(rf_random_aucrf$RFopt, type = 'prob')
otu_random_roc <- roc(Validate_early_euth_df$Euth_Early ~ otu_random_probs[ , 2])

random_aucrf_data <- Validate_early_euth_df[,c('Euth_Early',rf_random_aucrf$Xopt)]

#### 10-fold Cross validated - 10 repetitions
cv10r_aucs <- c()
cv10r_all_resp <- c()
cv10r_all_pred <- c()
for(j in 1:iters){
  set.seed(j)
  sampling <- sample(1:nrow(random_aucrf_data),nrow(random_aucrf_data),replace=F)
  cv10r_probs <- rep(NA,nrow(random_aucrf_data))
  for(i in seq(1,nrow(random_aucrf_data),5)){
    train <- random_aucrf_data[sampling[-(i:(i+4))],]
    test <- random_aucrf_data[sampling[i:(i+4)],]
    set.seed(seed)
    temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
    cv10r_probs[sampling[i:(i+4)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
  }
  cv10r_roc <- roc(random_aucrf_data$Euth_Early~cv10r_probs)
  cv10r_all_pred <- c(cv10r_all_pred, cv10r_probs)
  cv10r_all_resp <- c(cv10r_all_resp, random_aucrf_data$Euth_Early)
  cv10r_aucs[j] <- cv10r_roc$auc
}
cv10r_roc <- roc(cv10r_all_resp~cv10r_all_pred)

#### leave-one-out
LOOr_probs <- NULL
LOOr_probs <- sapply(1:nrow(random_aucrf_data), function(i){
 train <- random_aucrf_data[-i,]
  test <- random_aucrf_data[i,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOOr_probs[i] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOOr_roc <- roc(random_aucrf_data$Euth_Early~LOOr_probs)

#### leave-one-cage-out
LOcOr_df <- cbind(cage_id = Predict_df$cage_id, random_aucrf_data)
cage_list_random <- as.character(unique(LOcOr_df$cage_id))

LOcOr_probs <- NULL
LOcOr_probs <- sapply(1:length(cage_list_random), function(i){
  by_cage <- LOcOr_df$cage_id == cage_list_random[i]
  LOcO_predict <- select(LOcOr_df, -cage_id)
  train <- LOcO_predict[-by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOcOr_probs[[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
})
LOcOr_probs <- unlist(LOcOr_probs)
LOcOr_roc <- roc(random_aucrf_data$Euth_Early~LOcOr_probs)

#### plot rocs
par(mar=c(4,4,1,1))
plot(c(1,0),c(0,1), type='l', lty=3, xlim=c(1.01,0), ylim=c(-0.01,1.01), xaxs='i', yaxs='i', ylab='', xlab='')
plot(otu_random_roc, col='black', lwd=2, add=T, lty=1)
plot(cv10r_roc, col='gray', lwd=2, add=T, lty=1)
plot(LOOr_roc, col='blue', lwd=2, add=T, lty=2)
plot(LOcOr_roc, col='red', lwd=2, add=T, lty=2)
mtext(side=2, text="Sensitivity", line=2.5)
mtext(side=1, text="Specificity", line=2.5)
legend('bottomright', legend=c(sprintf('Out-Of-Bag (AUC: %.3g)',otu_random_roc$auc),
                               sprintf('Leave-1 mouse-out (AUC: %.3g)',LOOr_roc$auc),
                               sprintf('Leave-1 cage-out (AUC: %.3g)',LOcOr_roc$auc),
                               sprintf('10-fold CV (AUC: %.3g)',cv10r_roc$auc)),
#                               sprintf('OOB vs Leave-1-out: p=%.2g', roc.test(otu_random_roc,LOOr_roc)$p.value),
#                               sprintf('OOB vs 10-fold CV: p=%.2g', roc.test(otu_random_roc,cv10r_roc)$p.value)),
		lty=c(1,2,2,1,0,0), lwd=2, col=c('black','blue','red','gray'), bty='n')
```
